One more attempt on ArXe

### 2015-11-04 theo_results.tex
various stylistic changes

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Properties of simulated clusters.
{\it Q: Einheit von $\Gamma$? 
Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10${-6}$ aufzuschreiben, und diesen wegzulassen. 
Es w\"urde dadurch sehr viel \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.}
}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In small
clusters, are Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon
atoms in or on the cluster, the spectra are expected to be different.
As an example, we discuss the secondary electron spectra of 
clusters with a core of 13 argon atoms and two xenon atoms on different
surfaces. The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, 
simulated spectra are shown in Figure
\ref{figure:2tops}. Their xenon content is \unit[13.3]{\%} and thus
close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated coincidence spectra of argon clusters consisting of 13
          argon atoms with 2 additional xenon atoms on top of two different
          argon surfaces. The ICD and ETMD spectra are shown for all three
          different relative positionings of the two xenon atoms. In case of
          the two xenon atoms being close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the corresponding ICD spectrum.}
 \label{figure:2tops}
\end{figure}

In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peak due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the lower are the energies
of the secondary electrons and the smaller are the decay widths. 
{\it Q: war: `the higher are the decay widths', falschrum, oder?}
Therefore a
significant contribution from the ETMD(3) compared to the ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The threefold peak structure of the ETMD(3) peak does in contrast to
the ICD spectrum not stem from different triple structures but from the
four different decay channels for one triple structure.

For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
corresponds to six xenon atoms out of a total of 55 atoms. These can have
different relative positions in the cluster. They can either form a connected 
group in one part of the cluster or can be evenly distributed in the cluster,
as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/ar_3_6in.pdf}
 \caption{Simulated ICD and ETMD electron spectra for clusters consisting of
          55 atoms out of which 6 are xenon atoms. These are either clustered
          (group) on one side of the cluster of evenly distributed
          inside the cluster (scattered). In both cases the ETMD peaks are
          clearly visible in the spectra.}
 \label{figure:ar_3_6in}
\end{figure}

For both cases the overall ICD spectra are very similar with concoluted
peaks at approximately \unit[0.3]{eV}. For the grouped xenon atoms ICD
signals at slightly higher energies are to be observed from ArXe pairs of
larger distances du to the different cluster structure. However, the
significant difference is to be observed in the ETMD(3) spectra. The
interatomic xenon distance in the grouped xenon is shorther than in the
cluster with evenly distributed xenon atoms. Hence, the threefold
peak structure for the cluster with the grouped xenon atoms is seen at
lower ETMD(3) electron energies than for the cluster with evenly
distributed xenon atoms. Additionally, the probabilty for an electron
transfer from a xenon to an argon atom decreases exponentially with the
interatomic distance. Therefore, only those xenon atoms which have argon
atoms as their direct neighbours have a significant contribution to the
total decay width and the total ETMD(3) decay width for the structure with
the grouped xenon atoms is lower than the total ETMD(3) decay width of
the structure with evenly distributed xenon atoms.

For comparison with the previous assumptions of a xenon core surrounded
by argon atoms we investigated 13 and 55 atoms clusters with one or two
xenon atoms in the core. Some of the corresponding
spectra are shown in Figure \ref{figure:xe_3_in}.

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_3_in.pdf}
 \caption{Simulated ICD and ETMD electron spectra for argon clusters with
          one or two atoms in the core of the cluster. In case of the xenon
          atom inhabiting the central position of the cluster for a 13 atoms
          cluster (not shown here) and a 55 atoms cluster all channels are closed
          for all pairs, which leads to no signal. For those clusters with two
          xenon atoms in the core the first ICD channel is open for some pairs
          and additionally ETMD is possible for multiple triples. Due to a
          different distance distribution compared to the clusters with an argon
          core the ICD peak is shifted to higher kinetic energies.}
 \label{figure:xe_3_in}
\end{figure}

For the clusters with only one xenon atom in the core and the ionization
energies used for the simulation of the secondary electron energies
all ICD channels are closed. Since the cluster contains only one xenon atom,
an ETMD(3) is not possible. Hence there is no signal to be expected at all.
For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
can be seen. Compared to the argon core cluster structures the ICD peak is
shifted to higher ICD electron energies not being in agreement with
the experimental spectrum. Additionally, the ICD and ETMD(3) spectra overlap.
In case of the ETMD(3) only three of the four different decay channels are
anergetically allowed.

Originally, very large argon-xenon clusters were measured experimentally,
which we approximate by a cluster consisting of 1415 xenon atoms surrounded
by two complete layers of argon atoms. The spectra are shown in Figure
\ref{figure:xe_8_lay1}.

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
 \caption{Simulated ICD and ETMD electron spectra for a large cluster consisting
          of a xenon core of 1415 atoms surrounded by two complete layers of
          argon atoms. The ICD and ETMD peak overlap such, that the peak structure
          might not be visible.}
 \label{figure:xe_8_lay1}
\end{figure}

Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
the ICD peak is broadened and shifted to higher ICD electron energies which could be
expected due to the larger interatomic Ar-Xe distances in the large cluster and
the better stabilization of charges (the final state), which was taken care of
in the input of the simulation.
The ETMD(3) peak is as well shifted to slightly higher energies allowing for the
fourth decay channel to open.

>>>>

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Calculated properties of some model clusters. ICD, ETMD, and $\Gamma_{\rm ICD, ETMD}$ are the respective partial and total decay widths in 
{\it Q: Einheit von $\Gamma$? 
Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10$^{-6}$ aufzuschreiben, und diesen wegzulassen. 
Die Tabelle w\"urde dadurch \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.
Ich schlage weiterhin vor, statt $\Gamma_{\rm ICD, ETMD}$ das ratio $\Gamma_{\rm ETMD}/\rm total$ zu zeigen (ist glaube ich n\"utzlicher f\"ur die Diskussion).}
}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In small
clusters, are Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with 2 additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.
          {\it Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peak due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the lower are the energies
of the secondary electrons and the smaller are the decay widths. 
{\it Q: war: `the higher are the decay widths', falschrum, oder?}
Therefore a
significant contribution from the ETMD(3) compared to the ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The threefold peak structure of the ETMD(3) peak does in contrast to
the ICD spectrum not stem from different triple structures but from the
four different decay channels for one triple structure.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/ar_3_6in.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
          55 atoms, 6 out of which are xenon atoms. These are either grouped
          on one side of the cluster (label `group') or evenly distributed
          in the cluster interior (label `scattered').}
 \label{figure:ar_3_6in}
\end{figure}
%
For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
group in one part of the cluster or can be evenly distributed,
as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.

For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
In case that the xenon atoms are grouped, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distance.
A more significant difference is observed in the ETMD(3) spectra. 
The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
Additionally, the probability for an electron
transfer from a xenon to an argon atom decreases exponentially with the
interatomic distance. Therefore, only those xenon atoms which have argon
atoms as their direct neighbours have a significant contribution to the
total decay width, and the total ETMD(3) decay width is lower for the structure with
grouped xenon atoms than for
the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_3_in.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
          one or two xenon atoms in the core of the cluster (55 atoms total). 
          All ICD and ETMD channels are closed, if the cluster contains only 
          a single xenon atom. For clusters with two xenon atoms
          in the core, the first ICD channel is open for some pairs,
          and additionally ETMD is possible for multiple triples. Due to a
          different distance distribution compared to the clusters with an argon
          core (Figure \protect\ref{figure:2tops}), 
          the ICD peak is shifted to higher kinetic energies.}
 \label{figure:xe_3_in}
\end{figure}
%
For comparison with the previous assumptions of a xenon core surrounded
by argon atoms we investigated clusters of 13 and 55 atoms with one or two
xenon atoms in the core. Some of the corresponding
spectra are shown in Figure \ref{figure:xe_3_in}.

%For the clusters with only one xenon atom in the core and the ionization
%energies used for the simulation of the secondary electron energies
%all ICD channels are closed. Since the cluster contains only one xenon atom,
%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
shifted to higher ICD electron energies. 
Additionally, the ICD and ETMD(3) spectra overlap.
For ETMD(3), only three of the four different decay channels are
energetically allowed.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
          of a xenon core of 1415 atoms surrounded by one complete layer of
          argon atoms. {\it Q: War: `two complete layers' - bitte \"uberpr\"ufen.} The ICD and ETMD peak overlap such, that the peak structure
          might not be visible.}
 \label{figure:xe_8_lay1}
\end{figure}
%
In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
which we approximate by a cluster consisting of 1415 xenon atoms surrounded
by one layer of argon atoms. The spectra are shown in Figure
\ref{figure:xe_8_lay1}.

Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
the ICD peak is broadened and shifted to higher ICD electron energies which is
expected due to the larger interatomic Ar-Xe distances in the large cluster and
the better stabilization of charges (the final state), which has been taken into account
in the simulation.
The ETMD(3) peak is shifted to slightly higher energies as well, which allows opening of the
fourth decay channel.
